---  
title: "hierSCAL OM fit report"
geometry: letterpaper
nocaption: false
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{caption}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
always_allow_html: yes
params:
  rootDir: "~/Work/code/models/stockAssessment/multispecies/hierSCAL/Outputs/fits/fit_17042019212048"
  RdataFile: "fit_17042019212048.RData"
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: kable
    keep_md: false
  word_document:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
  bookdown::pdf_document2:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
    fig_width: 7
    fig_height: 6
  bookdown::html_document2:
    self_contained: true
    df_print: kable
    keep_md: false
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
  bookdown::word_document2:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
---

# Data Scenario and Model Hypothesis

```{r, setup, message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}

# I usually load my libraries up front to keep things organized
library(bookdown)
library(knitr)
library(kableExtra)
library(dplyr)
library(stringr)
library(PBSmapping)
library(tidyverse)
library(here)
# library( ggmap )
# library( maptools )
# library( rgdal )
# library( PBSmapping ) 
# library( RColorBrewer )
# library( RgoogleMaps)
# library( sp )
# library( raster )
# library( MASS )
# library( psyphy )
# library( boot )
# library( RCurl )
# library( scales )
# library( rgeos )
library( ggridges )
library( ggsidekick )

knitr::opts_knit$set(   fig.pos = 'p',
                        out.width = '100%', dpi=300, 
                        root.dir = params$rootDir,
                        message = FALSE, warning = FALSE, echo = FALSE )

options(warn = -1)

source(here("plots.R"))
source(here("SCALfuns.R"))
source(here("refPts.R"))

# Read in report file
repFilePath <- file.path(params$rootDir, params$RdataFile)
load(repFilePath)

repObj <- c(reports$repOpt, reports$data)
repObj <- calcRefPts(repObj)

repObj <- renameReportArrays(repObj = repObj, datObj = reports$data )

fYear   <- reports$fYear
nS      <- repObj$nS
nP      <- repObj$nP

```

Standard fit report for fits of hierSCAL to DERPA data.

Data Scenario: `r reports$ctlList$ctrl$dataScenarioName`

Model Hypothesis: `r reports$ctlList$ctrl$modelHypName`

Species: `r reports$ctlList$data$species`

Stocks: `r reports$ctlList$data$stocks`

```{r, captions, include = FALSE, echo = FALSE}
SBsptCaption <- "Spawning biomass (red line), catch (grey bars), and scaled biomass indices (coloured points), for all stocks and species. Indices are scaled by the fleet catchability, then by the ratio of spawning biomass to vulnerable biomass."

StdIdxCap   <- "Standardised vulnerable biomass (coloured lines) and the scaled and standardised biomass indices they are fitting to (coloured points), for all stocks and species."

IdxResCap   <- "Standardised residuals for model fits to biomass indices (coloured points) and a loess smoother with a 20% confidence interval (coloured lines and grey regions), for all fleets, stocks, and species."

RecPlotCap <- "Age-1 recruitments for all species and stocks. Equilibrium unfished recruitment $R_0$ is indicated by the horizontal dashed line."

RecDevPlotCap <- "Deviations from expected recruitment for all species and stocks."

YeqFCurvesCap <- "Equilibrium yield curves as a function of fishing mortality rates, assuming all fishing mortality comes from the modern trawl fleet."

ProbLenAgeCap <- "Probability curves of length-at-age for males (blue) and females (red). Curves show the probability of each length within an age group, and opacity of the lines increases with age."

tvqCap <- "Time series of observation model catchability (log-scale, coloured points) for the commercial fleets and Hecate Strait Multispecies Assemblage survey. Lines show the smoothed trend using a Loess smoother"

fishingMortCap <- "Estimates of fishing mortality from each fleet (coloured points and lines), gridded over species (columns) and stocks (rows). Fishing mortality rates are found using an iterative Newton-Rhapson solver conditioned on the observed catch."

modeledCatchCap <- "Modeled removals (blue points) using estimated fishing mortality compared to observed catches (open circles), gridded over species (columns) and stocks (rows)."

SRplotCap <- "Stock-recruit curves (solid lines) and modeled recruitments (grey points), gridded over species (columns) and stocks (rows)."

selLenCap <- "Selectivity-at-length for each fleet, gridded over species (columns) and stocks (rows). "

selAgeCap <- "Selectivity-at-age for each fleet, for females only, gridded over species (columns) and stocks (rows). "

```


# Full complex

## Spawning Biomass

```{r, plotSBall, echo = FALSE, message = FALSE, fig.cap = SBsptCaption }
plotSBspt( repObj = repObj, initYear = fYear)
```


## Fits to indices

```{r, idxFitsall, echo = FALSE, fig.cap = StdIdxCap }
plotScaledIdxGrid( repObj = repObj )

```

```{r, idxResidsAll, echo = FALSE, fig.cap = IdxResCap }
plotIdxResidsGrid( repObj = repObj )

```

## Recruitment

```{r, recruitments, echo = FALSE, fig.cap = RecPlotCap }
plotRspt( repObj = repObj, initYear = fYear )
```

```{r, recruitmentDevs, echo = FALSE, fig.cap = RecDevPlotCap }
plotRsptDev( repObj = repObj, initYear = fYear )
```

```{r, stockRecCurves, echo = FALSE, fig.cap = SRplotCap }
plotSRsp( repObj = repObj, initYear = fYear )
```


## Time-varying catchability

```{r, tvq, echo = FALSE, fig.cap = tvqCap }
plotTVq( repObj = repObj, sIdx = 1:nS, pIdx = 1:nP )
```

## Fishing mortality

```{r, fishingMortPlot, echo = FALSE, fig.cap = fishingMortCap }
  plotFspft( repObj = repObj, initYear = fYear )
```

```{r, catchFitPlot, echo = FALSE, fig.cap = modeledCatchCap }
  plotCatchFit_spt( repObj = repObj, initYear = fYear )
```


## Growth (Probability of Length-at-age)

```{r, plotProbLenAge, echo = FALSE, fig.cap = ProbLenAgeCap}
plotProbLenAge_sp(repObj)

```

## Selectivity

```{r, plotSelLength, echo = FALSE, fig.cap = selLenCap }
plotSelLen_spf(repObj = repObj, sIdx = 1:nS, pIdx = 1:nP )
```

```{r, plotSelAge, echo = FALSE, fig.cap = selAgeCap }
plotSelAge_spf(repObj = repObj, sIdx = 1:nS, pIdx = 1:nP )
```

## Reference Points

### Yield Curves

```{r, YeqFCurves, fig.cap = YeqFCurvesCap, echo = FALSE}
nS      <- repObj$nS
nP      <- repObj$nP
plotYeqF(repObj = repObj, sIdx = 1:nS, pIdx = 1:nP)


```


### Table

```{r, FmsyRefPtsTable, echo = FALSE}

FmsyRefPts <- repObj$refPts$FmsyRefPts

# need to combine these all into a table - also want B0/R0 etc


```


# Individual species

**UNDER CONSTRUCTION**

## Compositional data

## Growth


# Optimisation performance

## Phase fit table

```{r, phaseTable, echo = FALSE }
phaseReportTable <- reports$phaseList$fitReport

kable(  phaseReportTable, escape = FALSE, 
        caption = "Optimisation performance of hierSCAL for each phase.", booktabs = T,
        align = rep("c",ncol(phaseReportTable))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))

```
